Spokojnie — to jest znany problem independent researchers. Nie odrzucili paperu za jakość, tylko za brak afiliacji.

  Rozwiązania (od najszybszego)

  1. IGDORE — najszybsze (1-2 dni)

  Institute for Globally Distributed Open Research and Education — organizacja stworzona SPECJALNIE dla niezależnych badaczy. Dają oficjalną afiliację do publikacji.

  - Strona: https://igdore.org
  - Koszt: darmowe
  - Rejestracja online, weryfikacja 1-3 dni
  - Potem resubmit z: "Krzysztof Gwóźdź, IGDORE, Poland"
  - Setki independent researchers publikuje przez IGDORE na bioRxiv

  2. Ronin Institute — alternatywa

  Podobna organizacja dla independentów:
  - https://ronininstitute.org
  - Afiliacja: "Ronin Institute for Independent Scholarship"
  - Darmowe membership



Abstract: skopiuj ten tekst (to jest abstract z paperu):

  We introduce AlphaDynamics, a neural propagator for protein conformational dynamics operating directly on the backbone torsion manifold. The model couples N phase oscillators via learnable pairwise
  interactions and evolves them under a continuous ordinary differential equation solved by a fourth-order Runge-Kutta adjoint integrator. Final phases are mapped to a mixture of axis-independent von
  Mises densities through a shallow feed-forward head. Despite its compact size (348K parameters, roughly 1000-fold smaller than the 396M parameters of Timewarp), AlphaDynamics achieves a 57-out-of-57 win
   rate against a matched multilayer-perceptron baseline on the mdCATH benchmark, covering two size regimes (37 domains at 50 residues and 20 domains at 100 residues) under an identical simulation
  protocol (CHARMM36m + TIP3P water at 348 K, five replicas per domain). The mean NLL advantage is 5.4x at 50 residues and grows to 6.3x at 100 residues, with individual ratios reaching up to 21.7x on the
   most ordered domains. A 2500-step autoregressive rollout test shows that predicted trajectories remain stable and preserve per-residue Ramachandran distributions qualitatively. On a single RTX-5090
  AlphaDynamics generates one nanosecond of predicted trajectory in approximately 16 ms, corresponding to a 2000-fold speed-up over vacuum OpenMM simulation. Ablation experiments confirm that the ODE
  integration is the critical architectural component.

  Author Approvals: zaznacz obie checkboxy (approved + not published)




Ściągawka co wpisać

  Manuscript Basics:
  - Article Category: New Results
  - Subject Area: Biophysics
  - Title: AlphaDynamics: Coupled Phase Oscillators for Protein Torsion Dynamics Prediction

  Abstract: skopiuj z PDF (pierwsza sekcja paperu, od "We introduce AlphaDynamics..." do "...well-ordered proteins.")

  Author Approvals:
  - All authors approved: Yes (jesteś jedyny autor)
  - Accepted/published elsewhere: No
  - Competing interests: "The author declares no competing interests."





